---
title: "usaqmindia R package"
author: "Maëlle Salmon"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---
usaqmindia
=============
[![Build Status](https://travis-ci.org/masalmon/usaqmindia.svg?branch=master)](https://travis-ci.org/masalmon/usaqmindia)
[![Build status](https://ci.appveyor.com/api/projects/status/lujc2gn88smyvhrq?svg=true)](https://ci.appveyor.com/project/masalmon/usaqmindia)
[![codecov.io](https://codecov.io/github/masalmon/usaqmindia/coverage.svg?branch=master)](https://codecov.io/github/masalmon/usaqmindia?branch=master)


The U.S. Embassy and Consulates General in India maintain an air quality monitoring program with on-site measuring instruments and put the corresponding data [on this website](http://newdelhi.usembassy.gov/airqualitydata.html). There are csv files for 2013 and 2014, for 2015 except December which is in a pdf, and various csv/pdf for the months of the beginning of 2016. 

In this repository I have made a copy of these files and provide a R code for wrangling them to get a single csv with all measures for Delhi, Mumbai, Kolkata, Hyderabad and Chennai. Refer to original source for licensing questions. 

*Useful even for non R users: You will find the raw data [in this folder](inst/extdata) and my wrangling code is [here](inst/pm25_consulate.R). The resulting csv is [here](inst/pm25USA.csv). I will try to update the repository as new data comes in on the embassy website.*

I have made a R package out of the data so that my fellow R users can easily play with the data. The package imports [`ggTimeSeries`](https://github.com/Ather-Energy/ggTimeSeries) for doing the calendar plot. It can be installed this way:

```{r, eval = FALSE}
devtools::install_github("Ather-Energy/ggTimeSeries")
devtools::install_github("masalmon/usaqmindia")

```

The data is in a long format:

```{r, message=FALSE, warning=FALSE}
library("usaqmindia")
library("dplyr")
data("pm25_india")
pm25_india %>% head(n = 20) %>% knitr::kable()
```

Below is an example plot of concentrations (see the code [here](R/redo_plot.R)). Check out the Diwali peaks!

```{r, message=FALSE, warning=FALSE}
library("usaqmindia")
usaqmindia_plot()

```

And this is a calendar plot of daily median concentrations in one city using the [`ggTimeSeries`](https://github.com/Ather-Energy/ggTimeSeries) package (see the code [here](R/calendar.R)):

```{r, message=FALSE, warning=FALSE}
usaqmindia_calendar(cityplot = "Delhi")

```
